### 2016-02-06 paper.tex
modifications in MS-PUF section

{\flushleft \em Construction of MS-PUF. }
The MS-PUF is created by connecting an output of a DAC to an
input channel of an ADC. This creates a loop between the processor
core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
The sofware generates a challenge in the form of a time-series pattern
comprising of digital values, which are transferred one at a time
to the DAC. Each digital value is converted to an analog voltage or
current and reconverted to a representative digital value by the ADC.
The software program accumulates 
all ADC outputs to form the response to the challenge. Algorithm~\ref{algo:puf_sw}
has the details.

\begin{algorithm}[!ht] \label{algo:puf_sw}
\begin{scriptsize}
	\caption{\emph{Software Program for the MS-PUF}}
	\DontPrintSemicolon
	\KwIn{$\mathbf C$ : an array representing the challenge}
	\KwOut{$\mathbf R$ : an array representing the response}
	\Begin{
		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
			OutputToDAC($\mathbf C_i$); \\
			/* Wait for ADC to finish conversion */ \;
			$\mathbf R_i$ = InputfromADC(); \;	
		}
		\Return ${\mathbf R}$
	}
\end{scriptsize}
\end{algorithm}

Specify the PUF (formally)

Explain how the analysis is done

Why would we expect to have variation

A DAC output depends on several nano-scale features such 
as variations in voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have a in-built DAC, therefore
would be affected by the same variations as the DAC. Additionally,

Better PUFs by considering multiple devices

>>>>

{\flushleft \em Construction of the MS-PUF. }
The MS-PUF is created by connecting an output of a DAC to an
input channel of an ADC. This creates a loop between the processor
core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
The sofware running on the processor core 
generates a challenge in the form of a time-series pattern
comprising of $n$-bit digital values, which are transferred one at a time
to the DAC. Each digital value is converted to an analog voltage (or
current) and reconverted to a representative $m$-bit digital value by the ADC.
The software program reads the
ADC output and forms the response to the challenge using a function $g$.
Algorithm~\ref{algo:puf_sw} has the details.

\begin{algorithm}[!ht] \label{algo:puf_sw}
\begin{scriptsize}
	\caption{\emph{Software Program for the MS-PUF}}
	\DontPrintSemicolon
	\KwIn{$\mathbf C$ : an array representing the challenge}
	\KwOut{$\mathbf R$ : an array representing the response}
	\Begin{
		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
			Output\_to\_DAC($\mathbf C_i$); \\
			/* Wait for ADC to finish conversion */ \;
			$r$ = Input\_from\_ADC(); \;	
			$\mathbf R_i = g(C_i, r)$ \;
		}
		\Return ${\mathbf R}$
	}
\end{scriptsize}
\end{algorithm}

In every iteration in Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit reply from 
the ADC is the result of the $n$-bit DAC input $\mathbf C_i$
undergoing a conversion to analog followed by a reconversion to digital.
Typically $m$ and $n$ are $8$, $12$, $16$, or $24$ bits. 
Due to reasons such as quatification and ambient noise, the reply
$r$ would be different from $\mathbf C_i$. Further, due to nano-scale
variations between devices, $r$ would vary from one device
to another.  There are several potential reasons for variations 
between devices.
A DAC output for instance, is influenced by several nano-scale features such 
as voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have built in DACs, therefore
would be affected by the same variations as the DAC. Additionally,
other components in the ADC such as sample and hold circuits and
comparators could lead to differences in the reply.
